Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
table 3

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results}
We used various Reducer Nodes , simulation code and optimization algorithms in our experiments.
A summary is listed in Table~\ref{tab:built-in}
\begin{table*}
\centering
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}}
\hline 
Reducer Node & simulator & optimization\\
\hline 
Geometry Node & optics & \multirow{4}{4cm}{Error diffusion, SPSA, Branch and bound}\\
 InputMesh, Stratum, Column&
 Reflectance and transmittance, caustics\\ \cline{1-2}
Material Node & deformation  \\
Constant, Layered,QuadLayer, SubdivisionSufrace& 
non-linear elasticity
\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}
\subsection{Print Material Characterization and Measurement}
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

@@

\subsection{Textured Model}
Input: a textured 3D model and
measured Albedo of print material.

Output: (Probably gray-scale) Material arranged for different printers in different formats: STL, fable,Gcode.

Printers: Our printer, Makerbot, Objet, maybe Zcorp.

When printing texture, only the outer layer matters. We used 
a composition of two generators: a very high resolution grid
for the outer layer and a uniform material for the inside.

We expand the set of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}
\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height. We used a higher resolution
grid for the out layer and very low resolution
for the inner mesh.

>>>>

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results}
We used various Reducer Nodes , simulator and optimization algorithms in our experiments.
A summary of primitive components is listed in Table~\ref{tab:built-in}.
Table~\ref{tab:example} lists for each example, the components involved.
\begin{table*}
\centering
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}}
\hline 
Reducer Node & simulator & optimization\\
\hline 
Geometry Node & optics & \multirow{4}{4cm}{Error diffusion, SPSA, Branch and bound}\\
 InputMesh, Stratum, Column&
 Reflectance and transmittance, caustics\\ \cline{1-2}
Material Node & deformation  \\
ConstantMaterial, 
LayeredMaterial, QuadLayerMaterial, SubdivSurfMaterial & 
non-linear elasticity
\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}  %error metric is not interesting
\hline 
Example & Reducer Nodes & simulator & optimization\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
\hline
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
\hline 
Caustics 1 & Column, QuadLayerMaterial & & SA \\
\hline 
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
\hline
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:example}
\end{table*}

\subsection{Textured Model}
We expand the set of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}

%\subsection{Print Material Characterization and Measurement}
%We used existing measurements of Objet print materials.
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

@@

\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height. We used a higher resolution
grid for the out layer and very low resolution
for the inner mesh.
